### 2022-01-26 paper/main.tex
First draft of outline
This also creates the file structure for each of the chapters, which is nice

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

@@

	\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
	\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\

@@

\begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

	% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

	Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
	%Constant Name & $Symbol$ & $Constant Value$ with units\\

\end{constants}

@@

\begin{symbols}{lll} % Include a list of Symbols (a three column table)

	$a$ & distance & \si{\meter} \\
	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
	%Symbol & Name & Unit \\

	\addlinespace % Gap to separate the Roman symbols from the Greek

	$\omega$ & angular frequency & \si{\radian} \\

\end{symbols}

@@

\include{Chapters/Chapter1}
%\include{Chapters/Chapter2} 
%\include{Chapters/Chapter3}
%\include{Chapters/Chapter4} 
%\include{Chapters/Chapter5}

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
% final, % Uncomment to enable final mode (hide todos)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny,obeyFinal]{todonotes} % Todo notes in margin

\newcommand{\todosection}{\todo[linecolor=olive,backgroundcolor=olive!25,bordercolor=olive,inline]{TODO}}

@@

	\textbf{CRD} & \textbf{C}hrome \textbf{R}emote \textbf{D}esktop\\
	\textbf{PCB} & \textbf{P}rinted \textbf{C}ircuit \textbf{B}oard\\
	\textbf{RDP} & \textbf{R}emote \textbf{D}esktop \textbf{P}rotocol\\
	\textbf{SSH} & \textbf{S}ecure \textbf{Sh}ell (Protocol)\\
	\textbf{VNC} & \textbf{V}irtual \textbf{N}etwork \textbf{C}omputing\\

@@

% \begin{constants}{lr@{${}={}$}l} % The list of physical constants is a three column table

% 	% The \SI{}{} command is provided by the siunitx package, see its documentation for instructions on how to use it

% 	Speed of Light & $c_{0}$ & \SI{2.99792458e8}{\meter\per\second} (exact)\\
% 	%Constant Name & $Symbol$ & $Constant Value$ with units\\

% \end{constants}

@@

% \begin{symbols}{lll} % Include a list of Symbols (a three column table)

% 	$a$ & distance & \si{\meter} \\
% 	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
% 	%Symbol & Name & Unit \\

% 	\addlinespace % Gap to separate the Roman symbols from the Greek

% 	$\omega$ & angular frequency & \si{\radian} \\

% \end{symbols}

@@

\include{Chapters/Introduction}
\include{Chapters/Background}
\include{Chapters/StateOfTheArt}
\include{Chapters/Hardware}
\include{Chapters/Software}
\include{Chapters/Evaluation}
\include{Chapters/Conclusion}
